rbcL ASV clustering

### 2019-11-29 code/rbcl_asv_clustering.Rmd
changed object name
dark theme for omics presentation

conflicted::conflict_scout()
conflicted::conflict_prefer("filter","dplyr")
```

@@

final_tsne <- ggplot(tsne_rel_abund, aes(x=V1, y=V2)) +
  ggforce::geom_mark_ellipse(aes(fill=otu_name, label=otu_name), 
                             show.legend = FALSE, 
                             alpha=0, 
                             linetype="dashed", 
                             label.margin = margin(0,0,0,0,"mm"),
                             label.buffer = unit(1, "mm"),
                             label.fontface = "plain",
                             label.fontsize = 8,
                             con.type = "none",
                             expand = unit(2, "mm")) + # expansion of ellipse around points
  geom_point(aes(color = plot_taxa %>% fct_relevel(taxa.order), size = global_rel_abund, alpha=0.5))+
  labs(color="ASV taxonomic assignment", tag="B", title="t-SNE") +
  ggthemes::theme_few() +
  scale_size(range = c(2, 12), guide="none")

@@

mds <- ggplot(mds_asv_plot, aes(V1, V2)) + 
  ggforce::geom_mark_ellipse(data = mds_asv_plot %>% 
                               filter(otu_name != "Trebouxiophyceae J"), # dont plot the ellipse around other treb
                             aes(fill = otu_name, label=otu_name),
                             show.legend = FALSE, 
                             alpha=0, 
                             linetype="dashed", 
                             label.margin = margin(0,0,0,0,"mm"),
                             label.buffer = unit(1, "mm"),
                             label.fontface = "plain",
                             label.fontsize = 8,
                             con.type = "none",
                             expand = unit(2, "mm")) +
  geom_point(aes(color = plot_taxa %>% fct_relevel(taxa.order), size = global_rel_abund, alpha=0.5))+
  labs(color="ASV taxonomic assignment", tag="A",title="MDS") +
  ggthemes::theme_few() +
  scale_size(range = c(2, 12), guide="none")+
  guides(colour = guide_legend(override.aes = list(alpha = 1, size=3)), alpha="none") +
  theme(legend.position = "none") +
  scale_color_manual(values=taxa_colors, na.value=na_color)

@@

```{r, fig.width=4, fig.height=6}
asv_arranged <- gridExtra::grid.arrange(mds, tsne_no_legend, nrow=2)
```

@@

@@

# chlainomonas fasta for jordan
writeXStringSet(chlain_seqs, here("output/taxa_filtered_fastas/chlainomonas_otu.fasta"))
writeXStringSet(chlain_taxa_seqs, here("output/taxa_filtered_fastas/chlainomonas_idtaxa.fasta"))
```

>>>>

# conflicted::conflict_scout()
# conflicted::conflict_prefer("filter","dplyr")
```

```{r}
# theme_set(dark_theme_classic())
theme_set(dark_theme_light())
```

@@

final_tsne <- ggplot(tsne_rel_abund, aes(x=V1, y=V2)) +
  ggforce::geom_mark_ellipse(aes(fill=otu_name, label=otu_name), 
                             show.legend = FALSE, 
                             alpha=0, 
                             linetype="dashed", 
                             label.margin = margin(0,0,0,0,"mm"),
                             label.buffer = unit(1, "mm"),
                             label.fontface = "plain",
                             label.fontsize = 8,
                             con.type = "none",
                             expand = unit(2, "mm")) + # expansion of ellipse around points
  geom_point(aes(color = plot_taxa %>% fct_relevel(taxa.order), size = global_rel_abund, alpha=0.5))+
  labs(color="ASV taxonomic assignment", tag="B", title="t-SNE") +
  # ggthemes::theme_few() +
  scale_size(range = c(2, 12), guide="none")

@@

mds <- ggplot(mds_asv_plot, aes(V1, V2)) + 
  ggforce::geom_mark_ellipse(data = mds_asv_plot %>% 
                               filter(otu_name != "Trebouxiophyceae J"), # dont plot the ellipse around other treb
                             aes(fill = otu_name, label=otu_name),
                             show.legend = FALSE, 
                             alpha=0, 
                             linetype="dashed", 
                             label.margin = margin(0,0,0,0,"mm"),
                             label.buffer = unit(1, "mm"),
                             label.fontface = "plain",
                             label.fontsize = 8,
                             con.type = "none",
                             expand = unit(2, "mm")) +
  geom_point(aes(color = plot_taxa %>% fct_relevel(taxa.order), size = global_rel_abund, alpha=0.5))+
  labs(color="ASV taxonomic assignment", tag="A",title="MDS") +
  # ggthemes::theme_few() +
  scale_size(range = c(2, 12), guide="none")+
  guides(colour = guide_legend(override.aes = list(alpha = 1, size=3)), alpha="none") +
  theme(legend.position = "none") +
  scale_color_manual(values=taxa_colors, na.value=na_color)

@@

```{r, fig.width=4, fig.height=6}
asv_arranged <- gridExtra::grid.arrange(mds, tsne_no_legend_nice_colors, nrow=2)
```

```{r, fig.width=7, fig.height=3.5}
present_version <- gridExtra::grid.arrange(mds, tsne_no_legend_nice_colors, ncol=2)
```

@@

# write black formatted versions for presentation
ggsave(filename = here("presentation/omics/asvs.pdf"), plot=present_version, width = 7, height = 3.5)
ggsave(filename = here("presentation/omics/asv_legend.pdf"), plot=legend,  height = 4, width = 2.2)

@@

# chlainomonas fasta for jordan
writeXStringSet(chlain_seqs, here("output/taxa_filtered_fastas/chlainomonas_otu.fasta"))
writeXStringSet(chlain_taxa_seqs, here("output/taxa_filtered_fastas/chlainomonas_idtaxa.fasta"))
